
\documentclass[11pt,notitlepage]{article}

\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{wrapfig} % Allows in-line images
\usepackage[labelfont=bf]{caption} % Make figure numbering in captions bold
\usepackage{graphicx} % Required for including images
\usepackage[top=0.7in,bottom=1in,left=1in,right=1in]{geometry}
\pagestyle{empty} % Remove page numbering

\hyphenation{ionto-pho-re-tic iso-tro-pic fortran} % Specifies custom hyphenation points for words or words that shouldn't be hyphenated at all

\renewcommand{\thesection}{\Roman{section}}

\begin{document}

\vspace*{0.5cm}

\noindent{\fontsize{16}{19.2}\selectfont \textbf{Current Experiment}}

\vspace{1cm}
\textbf{Problem, Relevance, Solution}\\
Problem: DF values unknown\\
Relevance: Interdicted Material Origins\\
Solution: Determine DF values, and link to D-values

%------------------------------------------------------------
%	Introduction
%------------------------------------------------------------
 
\section{Problems with Previous Experiment}
\begin{enumerate}
\item{Concentrations too low in Mass-Spec and Gamma}
  \begin{itemize}
  \item{Some previous data just didn't make sense}
  \end{itemize}
\item{Barium contamination}
\item{Experiment contamination (vials too tall)}
\item{Activity Balance}
\item{Lack of full molecular separation of phases before partition.}
\end{enumerate}

%------------------------------------------------------------
%	Objectives
%------------------------------------------------------------

\section{How current experiment attempted to address problems}
\begin{enumerate}
\item{Factor of four concentration increase}
  \begin{itemize}
  \item{Factor of 2 from initial solution}
  \item{Factor of 2 from less initial volume (also lets us switch
  to smaller vials for first cycle)}
  \end{itemize}
\item{Leech vials before use}
\item{Switch to vials with smaller height/diameter (also have nice push caps)
  for first cycle}
\item{Maintain constant geometry for gamma counts}
\item{Centrifuge samples after agitation on vortex mixer}
\end{enumerate}

%------------------------------------------------------------
%	Present Status of the Question
%------------------------------------------------------------

\section{Status of experiment}

Problem with first extraction. Exploding top after vortex mix,
Sputtering pipette, contamination, 2-3 drops lost.
Chemistry for cycle one is complete.
Counted 4 different vials, still need to count 2 more.
No alpha samples as of yet.

%------------------------------------------------------------
%	Procedure
%------------------------------------------------------------

\section{Prelinary Results}
Reduction of Cs by...

\section{Next Week}
Full analysis of cycle one gamma and alpha.
Cycle 2 complete, at a similar stage as this week. 

%------------------------------------------------------------
%	Bibliography
%------------------------------------------------------------

%\bibliography{references} %
%\bibliographystyle{plain} % 

%----------------------------------------------------------------------------------------

\end{document}
